Manuscript progress report

### 2023-12-22 Docs/manuscript.Rmd
small scale simulation 500 iterations

```{r}
M2 <- length(pred_subset_fGFPCA)
## ISE container 
ise_mat_subset <- ise_mat_subset_ref <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M2))
```

```{r ise_fGFPCA_subset}
for(m in 1:M2){
  this_df <- pred_subset_fGFPCA[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_mat_subset[,,m] <- ise_tb_m
}

@@

```{r ise_GLMMadaptive_subset}
for(m in 1:M2){
  this_df <- pred_subset_adglmm[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_mat_subset_ref[,,m] <- ise_tb_m
}

@@

```{r}
## auc container 
auc_mat_subset <- array(NA, dim = c(length(window)-2, length(window)-2, M2))
auc_mat_subset_ref <- array(NA, dim = c(length(window)-2, length(window)-2, M2))
```

```{r auc_fGFPCA_subset}
for(m in 1:M2){
  this_df <- pred_subset_fGFPCA[[m]]

@@

```{r auc_GLMMadaptive_subset}
for(m in 1:M2){
  this_df <- pred_subset_adglmm[[m]]

@@

There is huge difference in compuation time. GLMMadaptive took 23 minutes, while fGFPCA took less than 3 seconds.

```{r}
data.frame(
  "Method" = c("fGFPCA", "GLMMadaptive"),
  "Fit" = c(mean(fit_time_subset_fGFPCA)/60, mean(fit_time_subset_adglmm)),
           "Prediction"= c(mean(pred_time_subset_fGFPCA), mean(pred_time_subset_adglmm)/60)) %>%
  kable(digits = 3, caption = "Computation time (minutes)", booktabs = T) %>%
  kable_styling(full_width = F) 
```

>>>>

```{r}
# M2 <- length(pred_subset_fGFPCA)
## ISE container 
ise_mat_subset <- array(NA, dim = c(length(window)-2, length(window)-2, length(pred_subset_fGFPCA)))

pred_subset_adglmm <- pred_subset_adglmm[num_probs==0]
ise_mat_subset_ref <- array(NA, dim = c(length(window)-2, length(window)-2, length(pred_subset_adglmm)))

```{r ise_fGFPCA_subset}
for(m in 1:length(pred_subset_fGFPCA)){
  this_df <- pred_subset_fGFPCA[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_mat_subset[,,m] <- ise_tb_m
}

@@

```{r ise_GLMMadaptive_subset}
for(m in 1:length(pred_subset_adglmm)){
  this_df <- pred_subset_adglmm[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_mat_subset_ref[,,m] <- ise_tb_m
}

@@

```{r}
## auc container 
auc_mat_subset <- array(NA, dim = c(length(window)-2, length(window)-2, 
                                    length(pred_subset_fGFPCA)))
auc_mat_subset_ref <- array(NA, dim = c(length(window)-2, length(window)-2, 
                                        length(pred_subset_adglmm)))
```

```{r auc_fGFPCA_subset}
for(m in 1:length(pred_subset_fGFPCA)){
  this_df <- pred_subset_fGFPCA[[m]]

@@

```{r auc_GLMMadaptive_subset}
for(m in 1:length(pred_subset_adglmm)){
  this_df <- pred_subset_adglmm[[m]]

@@

Among 500 hundred iterations, `r sum(num_probs)` did not converge for the GLMMadaptive model. No numeric issue for fGFPCA.

```{r}
data.frame(
  "Method" = c("fGFPCA", "GLMMadaptive"),
  "Fit" = c(mean(fit_time_subset_fGFPCA)/60, mean(fit_time_subset_adglmm, na.rm=T)),
           "Prediction"= c(mean(pred_time_subset_fGFPCA), mean(pred_time_subset_adglmm, na.rm=T)/60)) %>%
  kable(digits = 3, caption = "Computation time (minutes)", booktabs = T) %>%
  kable_styling(full_width = F) 
```
